\section{COTS Components and Technical Constraints}
Android \cite{Android} is a Linux based operation system developed by Open Handset Alliance. It runs on smart phones, computer tablets and mobile devices. Android is open source, and developers writes in a customized version of Java\cite{sdk}. In addition to original Android, our project involves the usage of Skiller\cite{Skiller}, which is a platform help develop networking multiplayer games. Skiller provides multiple tools to implement social and game-additive features, such as achivements and in-game items and much more.

% In addition to Android, our project involves Open Feint, which is a multi-player game framework.??? [x]
\subsection{Android activities}
An android application is build up with activities that represents what you see on the screen. Normally an activity holds a view which is made in xml, that means we need to be aware of the usage of custom java views. Since we have planned a MVC structure in our game we also need to be aware of androids internal MVC structure, which can be counterproductive to avoid.

\subsection{Touch screen}
Android smart phones all have touch screens, therefore its very important that the game must be designed in a way that it interacts well with the screen constraints. Both the physical buttons and the touch menus must be designed in a way so that the user understand what they press.

\subsection{Screen resolution}
Android smart phones have different screen resolution, in this project we will test the application with a Samsung Galaxy SII, HTC Desire and Samsung Galaxy Nexus. All phones use the same resolution but the the Galaxy SII and Nexus has much bigger screens, the limited resolutions and screen size will require a precise and well designed layout.

\subsection{Android device game only}
The game will only be able to run successfully on Android smart phones.

%\subsection{App engine?

%\subsection{Open feint?}
