\section{Introduction}
This course teaches architectural styles and patterns, methods for constructing and evaluating architectures, and comnponent-based development. Design patterns and object-oriented frameworks are also covered. \\

The goal of this project is to develop a fully functional two player version of the classic board game \emph{Nine Men's Morris}, using the methods and styles corresponding with the course goals. \\

According to the recommended practice of IEEE 1471, this document details architectural patterns and tactics based on all of the underlying drivers, stakeholders and their concerns. The 4+1 View model is a recommended practice for architecture description of software-intensive systems, and will be used to describe the system from the viewpoint of different stakeholders, such as end-users, developers and project managers. \\

The second chapter will cover the architectural drivers for this project. The third chapter will cover stakeholders and concerns, while the fourth chapter contains a selection of architectural viewpoints. Architectural tactics and architectural patterns will be covered in chapter five and six, respectively. The seventh chapter contains a selection of views. This includes a logical view with a class diagram, a development view, a process view with an activity diagram, and lastly a physical view showing how our system interacts with a third party server solution. Chapter eight concerns the consistency among our views, and the following chapters cover architectural rationale, issues, document changes and at last references.



