

\section{Architectural tactics}

\subsection{Modifiability}                       

\subsubsection{Prevention of Ripple Effect}
The code should contain as few dependencies as possible in order to avoid ripple effect when making changes to the code.

\subsubsection{Localize Changes}
As our quality requirements highlight in the Requirements Document \cite{requirement}, we have anticipated several possible extensions to our game application. We have taken this into account, and will build our architecture with this in mind.

\subsection{Usability}

\subsubsection{Design-time tactics}
\begin{itemize}
\item The GUI will be separated from the model, thus making it easy to carry out changes that only concerns the graphical layout.
\item The system will use a third party server solution for the multiplayer feature, which makes the job easier for the developers.
\end{itemize}

\subsubsection{Runtime tactics}
\begin{itemize}
\item The system shall, as mentioned in the functional requirements, highlight the user's possible moves.
\item The system shall inform the user whose turn it is during gameplay. 
\end{itemize}

\subsubsection{Others}

\begin{itemize}
\item To optimize the usability of our user interface, we will get feedback from outside users during the project.
\item We will follow the Android user interface guidelines. These design principles were developed by and for the Android User Experience Team to keep users' best interests in mind. We will consider them as we apply your own creativity and design thinking.
\end{itemize}

%\subsubsection{User feedback between implementation iterations}

%\subsubsection{Follow the Android user interface guidelines} 
%These design principles were developed by and for the Android User Experience Team to keep users' best interests in mind. We will consider them as we apply your own creativity and design thinking.

%\subsection{Testability}
%\subsubsection{Testing third party multiplayer connection}
%The application uses a third party multiplayer feature. This makes connection testing easy, as it is detached from the rest of the application.